High-order Solution Transfer between Curved Triangular Meshes

### 2020-04-30 doc/paper.tex
Adding citation for "Spatially accelerated shape embedding in multimaterial simulations" as a way to speed up the brute-force search for pairs of mesh elements.
Adding `Anderson2018` citation.
It is unused for now, but will be referenced shortly. Also
removing a stray `'`.'

In either case, the change in the
mesh between time steps requires transferring a known solution on the
discarded mesh to the mesh produced by the remeshing process. Without
the ability to change the mesh, Lagrangian methods (or, more generally,
ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
(the Lagrangian approach) and typically combine the benefits of both approaches
to create composite methods} \cite{Hirt1974}) would not be useful, since after '
a limited time the mesh will distort.

@@

For special cases, e.g. ALE methods, the initial brute-force search
can be reduced to \(\bigO{1}\). This could be enabled by tracking
the remeshing process so a correspondence already exists. If a full
mapping from donor to target mesh exists, the process of computing
\(M_T\) and \(M_{TD} \bm{d}\) can be fully parallelized across
elements of the target mesh, or even across shape functions
\(\phi_T^{(j)}\).

>>>>

In either case, the change in the
mesh between time steps requires transferring a known solution on the
discarded mesh to the mesh produced by the remeshing process. Without
the ability to change the mesh, Lagrangian methods (or, more generally,
ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
(the Lagrangian approach) and typically combine the benefits of both approaches
to create composite methods} \cite{Hirt1974}) would not be useful, since after
a limited time the mesh will distort.

@@

For special cases, e.g. ALE methods, the initial brute-force search
can be reduced to \(\bigO{1}\). This could be enabled by tracking
the remeshing process so a correspondence already exists. If a full
mapping from donor to target mesh exists, the process of computing
\(M_T\) and \(M_{TD} \bm{d}\) can be fully parallelized across
elements of the target mesh, or even across shape functions
\(\phi_T^{(j)}\). Spatial binning techniques for mesh elements could also be
used to improve the initial brute-force search as in \cite{Weiss16_imr}.
